Identifying Software Performance Changes Across Variants and Versions

### 2020-08-07 paper.tex
replaced tildes wih commas

 	\subsubsection{Acquiring Configurations}
 	The exploration of new configurations is similar to the initial sample selection strategy (distance-based sampling) described in Section~\ref{sec:initialization}. We select a constant number of configurations (default value: 75) for exploration. The exploitation of new configurations requires additional constraints. We define the following constraints for exploiting the candidate solution's associations. For each commit in the candidate solution, we perform exploitation in two directions. For the first direction, at least 80~\% of  configuration options associated with a commit are required to be selected, whereas, for the second direction, at least 80~\% configuration options not associated with a commit are required to be selected. This way, we limit variation among configuration options. The first direction aims at enabling additional configuration options to search for previously unseen associations (under-approximation). The second direction aims at the opposite: We limit variation to those configuration options already associated with a commit and therefore search for configuration options that are falsely associated (over-approximation). We use the limit of 80~\% to allow a broader scope of valid configurations to be sampled by a constraint solver. For each new configuration, we assess performance for randomly selected commits.

 	We limit the total number of new measurements per iteration with a budget $n_\text{measurements}$. This budget is split between acquisition for commits and configurations with a factor $n_\text{commits\_to\_configs} = 0.5$. The measurement budget for commit acquisition is further split between exploration and exploitation with a factor $n_\text{commit\_explore} = 0.5$. That is, initially, 50~\% of the budget are used for configuration acquisition and 25~\% for commit exploration and exploitation, respectively. As the algorithm proceeds, we multiply the factor $n_\text{commits\_to\_configs}$ by 0.95 and the factor $n_\text{commits\_explore}$ by 0.9. That is, the algorithm shifts  (1) towards sampling configurations in depth and (2) focuses on exploitation in later iterations. The rationale is that we consider pinpointing commit to configuration options a more difficult task than finding performance-changing commits.

@@

	\subsubsection{Influence of System Size}
	We are interested in how the size of a configurable software system influences the accuracy and efficiency of our approach. 
	To answer this question, we synthesize performance data for systems of varying size in terms of number of configuration options and the number of commits. For the number of configurations $n_\text{options}$, we selected a range that resembles configurable software systems studied in previous work~\cite{muhlbauer_accurate_2019}; similarly, we selected a range for the number of commits $n_\text{commits}$ to cover young as well as mature software systems. We present the ranges of the two parameters in Table~\ref{tab:synthetic_experiment_ranges}.

@@

	As the distribution in Figure~\ref{fig:results_rq1_frequency} illustrates, most experiments terminated after the minimum of three iterations or with less than 29 iterations. That is, most experiments reached our termination criterion. 
	Regarding the measurement effort, for small systems with 8 configuration options, we required up to 50~\% of all possible measurements. By contrast, for greater systems, the required measurement effort was well below 1~\%. The high reported measurement effort for systems with 8 configuration options is due to our choice of the measurements per iterations, which vastly over-approximates. Since we are able handle systems with more configuration options with similar effort, we are confident, that a smaller number of measurements per iteration would reduce the relative measurement effort required substantially.

@@

	\begin{quotation}
		''\texttt{\footnotesize liblzma: Adjust default depth calculation for \textbf{HC3} and \textbf{HC4}. [...]}`` (revision 626 of \textsc{xz})\\
		''\texttt{\footnotesize Use ffsl for a \textbf{faster} lesser\_bitness function.}`` (revision 521 of \textsc{lrzip})
	\end{quotation}

>>>>

 	\subsubsection{Acquiring Configurations}
 	The exploration of new configurations is similar to the initial sample selection strategy (distance-based sampling) described in Section~\ref{sec:initialization}. We select a constant number of configurations (default value: 75) for exploration. The exploitation of new configurations requires additional constraints. We define the following constraints for exploiting the candidate solution's associations. For each commit in the candidate solution, we perform exploitation in two directions. For the first direction, at least 80\,\% of  configuration options associated with a commit are required to be selected, whereas, for the second direction, at least 80\,\% configuration options not associated with a commit are required to be selected. This way, we limit variation among configuration options. The first direction aims at enabling additional configuration options to search for previously unseen associations (under-approximation). The second direction aims at the opposite: We limit variation to those configuration options already associated with a commit and therefore search for configuration options that are falsely associated (over-approximation). We use the limit of 80\,\% to allow a broader scope of valid configurations to be sampled by a constraint solver. For each new configuration, we assess performance for randomly selected commits.

 	We limit the total number of new measurements per iteration with a budget $n_\text{measurements}$. This budget is split between acquisition for commits and configurations with a factor $n_\text{commits\_to\_configs} = 0.5$. The measurement budget for commit acquisition is further split between exploration and exploitation with a factor $n_\text{commit\_explore} = 0.5$. That is, initially, 50\,\% of the budget are used for configuration acquisition and 25\,\% for commit exploration and exploitation, respectively. As the algorithm proceeds, we multiply the factor $n_\text{commits\_to\_configs}$ by 0.95 and the factor $n_\text{commits\_explore}$ by 0.9. That is, the algorithm shifts  (1) towards sampling configurations in depth and (2) focuses on exploitation in later iterations. The rationale is that we consider pinpointing commit to configuration options a more difficult task than finding performance-changing commits.

@@

	\subsubsection{Influence of System Size}
	We are interested in how the size of a configurable software system influences the accuracy and efficiency of our approach. 
	To answer this question, we synthesize performance data for systems of varying size in terms of number of configuration options and the number of commits. For the number doppel of configurations $n_\text{options}$, we selected a range that resembles configurable software systems studied in previous work~\cite{muhlbauer_accurate_2019}; similarly, we selected a range for the number of commits $n_\text{commits}$ to cover young as well as mature software systems. We present the ranges of the two parameters in Table~\ref{tab:synthetic_experiment_ranges}.

@@

	As the distribution in Figure~\ref{fig:results_rq1_frequency} illustrates, most experiments terminated after the minimum of three iterations or with less than 29 iterations. That is, most experiments reached our termination criterion. 
	Regarding the measurement effort, for small systems with 8 configuration options, we required up to 50\,\% of all possible measurements. By contrast, for greater systems, the required measurement effort was well below 1\,\%. The high reported measurement effort for systems with 8 configuration options is due to our choice of the measurements per iterations, which vastly over-approximates. Since we are able handle systems with more configuration options with similar effort, we are confident, that a smaller number of measurements per iteration would reduce the relative measurement effort required substantially.

@@

	\begin{quotation}
		"\texttt{\footnotesize liblzma: Adjust default depth calculation for \textbf{HC3} and \textbf{HC4}. [...]}" (revision 626 of \textsc{xz})\\
		"\texttt{\footnotesize Use ffsl for a \textbf{faster} lesser\_bitness function.}" (revision 521 of \textsc{lrzip})
	\end{quotation}
